High-Performance Language Primitives for Distributed Architectures using Asynchronous Events

### 2012-07-23 doc/asplos2013/related.tex
Minor edits

Chapel\cite{Chamberlain:Chapel} and X10\cite{X1005} are high-level parallel
programming languages that support asynchronous operations.  The constructs
introduced in these languages are higher-level and have complex 
semantics.  We view our interface as providing a potential target
for implementing these higher-level asynchronous operations in an efficient
manner similar to Legion\cite{Legion12}.

>>>>

Chapel\cite{Chamberlain:Chapel} and X10\cite{X1005} are high-level parallel
programming languages that support asynchronous operations.  The constructs
introduced in these languages are higher-level and have complex 
semantics.  We view our interface as providing a target
for implementing these higher-level asynchronous operations in an efficient
manner similar to Legion\cite{Legion12}.

Physical regions in our interface are related to
arrays from the Sequoia runtime interface\cite{Houston08} in that they
both allow the runtime to do specialized operations on data by being
aware of the structure of data.  Sequoia's runtime interface supported
asynchronous tasks and copies, but did not permit composition of
asynchronous operations.
